The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with {\em Gaia} Data and Beyond

### 2019-04-25 paper/ms.tex
Update author list, acknowledgements
Update Table 1 w more info about actions

@@

\author{others}

@@

\begin{deluxetable*}{cCCCCCCCC}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within
$250\,\pc$ of the Sun, using the relevant initial positions and velocities
from \citet{2018AA...616A..10G}. The neighborhood column is explained in more
detail in Section~\ref{sssec:reconstruction}.\label{tab:real_clusters}}
\tablehead{\colhead{cluster} & \colhead{$N_{\text{memb}}$} & \colhead{distance} & \colhead{$J_R$} &
\colhead{$J_{\phi}$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} & \colhead{neighborhood} \\ 
\colhead{ } & \colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$} & \colhead{$\mathrm{pc}$}}
\startdata
alphaPer & 740 & 174.9 & \sim20 & \sim -1700 & \sim0.005 & \sim11 & 352\tablenotemark{b} & 57 \\
Blanco1 & 489 & 237.2 & \sim2 & \sim-1800 & \sim2 & \sim210 & 410\tablenotemark{c} & 1460 \\
ComaBer & 153 & 85.9 & \sim2 & \sim-1900 & \sim0.7 & \sim140 & 112\tablenotemark{d} & 522\\
Hyades & 515 & 47.5 & \sim20 & \sim-1800 & \sim0.3 & \sim80 & 400\tablenotemark{e} & 462 \\
IC2391 & 325 & 151.6 & \sim6 & \sim-1800 & \sim0.02 & \sim20 & \nodata & \nodata \\
IC2602 & 492 & 152.2 & \sim10 & \sim-1700 & \sim0.3 & \sim89 & \nodata & \nodata \\
NGC2451A\tablenotemark{a} & 400 & 193.7 & \sim6 & \sim-1800 & \sim0.2 & \sim73 & \nodata & \nodata \\
Pleiades & 1326 & 135.8 & \sim20 & \sim-1700 & \sim0.4 & \sim96 & 800\tablenotemark{f} & 685 \\
Praesepe & 938 & 186.2 & \sim20 & \sim-1800 & \sim0.6 & \sim120 & 550\tablenotemark{d} & 781
\enddata

@@

\acknowledgments
We would like to thank Megan Bedell, Tobias Buck, Elena D'Onghia, Benoit
Famaey, and Adrian Price-Whelan for helpful discussions. A.B. would like to
thank Todd Phillips for helpful discussions. A.B. was supported in part by the
Roy \& Diana Vagelos Program in the Molecular Life Sciences and the Roy \&
Diana Vagelos Challenge Award.
%mm The work of \Gus{everyone} is supported by the Simons
%Foundation. \Gus{remove last sentence if everyone CCA affiliated}
M.-M.M.L. was partly supported by NSF grant AST18-15461.

>>>>

\author{Kathryn V. Johnston}
\affil{\columbia}

@@

\author{Douglas Filho}
\affil{\columbia}

\author{David W. Hogg}
\affil{\nyuphys}
\affil{\nyucds}
\affil{\cca}
\affil{\mpia}

\author{Chervin F. P. Laporte}
\altaffiliation{Simons Fellow}
\affil{\victoria}

@@

\begin{deluxetable*}{cCCCCCCCC}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within
$250\,\pc$ of the Sun, using the relevant initial positions and velocities
from \citet{2018AA...616A..10G}. Actions are computed using the method outlined in Section~\ref{ssec:action_comp}, with typical values for the Galactocentric coordinate system parameters. These are only shown to illustrate the general types of orbits open clusters are on. The neighborhood column is explained in more
detail in Section~\ref{sssec:reconstruction}.\label{tab:real_clusters}}
\tablehead{\colhead{cluster} & \colhead{$N_{\text{memb}}$} & \colhead{distance} & \colhead{$J_R$} &
\colhead{$J_{\phi}$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} & \colhead{neighborhood} \\ 
\colhead{ } & \colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$} & \colhead{$\mathrm{pc}$}}
\startdata
alphaPer & 740 & 174.9 & 20 & -1700 & 0.005 & 11 & 352\tablenotemark{b} & 57 \\
Blanco1 & 489 & 237.2 & 2 & -1800 & 2 & 210 & 410\tablenotemark{c} & 1460 \\
ComaBer & 153 & 85.9 & 2 & -1900 & 0.7 & 140 & 112\tablenotemark{d} & 522\\
Hyades & 515 & 47.5 & 20 & -1800 & 0.3 & 80 & 400\tablenotemark{e} & 462 \\
IC2391 & 325 & 151.6 & 6 & -1800 & 0.02 & 20 & \nodata & \nodata \\
IC2602 & 492 & 152.2 & 10 & -1700 & 0.3 & 89 & \nodata & \nodata \\
NGC2451A\tablenotemark{a} & 400 & 193.7 & 6 & -1800 & 0.2 & 73 & \nodata & \nodata \\
Pleiades & 1326 & 135.8 & 20 & -1700 & 0.4 & 96 & 800\tablenotemark{f} & 685 \\
Praesepe & 938 & 186.2 & 20 & -1800 & 0.6 & 120 & 550\tablenotemark{d} & 781
\enddata

@@

\acknowledgments
We would like to thank Megan Bedell, Tobias Buck, Elena D'Onghia, Benoit
Famaey, and Adrian Price-Whelan for helpful discussions. A.B. would like to
thank Todd Phillips for helpful discussions. A.B. was supported in part by the
Roy \& Diana Vagelos Program in the Molecular Life Sciences and the Roy \&
Diana Vagelos Challenge Award. M.-M.M.L. was partly supported by NSF grant
AST18-15461. The work of D.A.-A., A.B., D.W.H., C.F.P.L., R.S., K.V.J.,
M.-M.M.L., and M.K.N. is supported by the Simons Foundation.
